---
title: "Titantic - Exploratory Analysis"
author: "Chloe"
date: "10/13/2016"
output: 
  html_document:
    toc: true
---

<style>
  body {
    background: #F0F0F0;
  }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r prep, message=FALSE, warning=FALSE, include=FALSE}

#clear environment if needed
rm(list = ls())

#set working directory
setwd('~//Documents/Dev_dataScienceProjects/1.Titanic_machineLearning_Kaggle')

#laod data
train <- read.csv("./Data/train.csv",stringsAsFactors = F)
test <- read.csv("./Data/test.csv",stringsAsFactors = F)

#combine dataset for exploratory analysis
#take out Survived from train set
master <- rbind(train[,-2],test)

#install/reuqire libraries
pacman::p_load("ggplot2","data.table","dplyr")

```

## Overview


### Hypotheses



## Data
### Variable Descriptions

|Variable |Descriptions                                                        |
|--------:|-------------------------------------------------------------------:|
|survival |Survival (0 = No; 1 = Yes)                                          |
|pclass   |Passenger Class (1 = 1st; 2 = 2nd; 3 = 3rd)                         |
|name     |Name                                                                |
|sex      |Sex                                                                 |
|age      |Age                                                                 |
|sibsp    |Number of Siblings/Spouses Aboard                                   |
|parch    |Number of Parents/Children Aboard                                   |
|ticket   |Ticket Number                                                       |
|fare     |Passenger Fare                                                      |
|cabin    |Cabin                                                               |
|embarked |Port of Embarkation (C = Cherbourg; Q = Queenstown; S = Southampton)|

```{r datatype, message=FALSE, warning=FALSE, include=FALSE}
#transform data type into correct format
#since this dataset has few variables
col_char=c("PassengerId","Name","Ticket") #select columns that need to be transformed to factor
                master[col_char] <- lapply(master[col_char], character)
                
                

col_fact=c("Pclass","Cabin","Embarked") #select columns that need to be transformed to factor
                master[col_fact] <- lapply(master[col_fact], factor)



```

### Basic Statistics
- Dataset includes total of __`r dim(master)[1]`__ records with __`r dim(master)[2]`__ independent variables, and __survival__ as dependent variable.
- Examine missing values (graphs)
    + Treatment of missing values
    + Age: imputation
    + Fare:


